\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-01-21 paper/m-lb-m-technometrics.tex
Change to title, edits related to marginal conditional quantile distinction

\if0\blind
{
  \title{\bf A hierarchical failure-time model for heterogenous field data}
  \author{Eric Mittman\thanks{Department of Statistics, Iowa State University}\\
    and \\
    Colin Lewis-Beck\footnotemark[1]\\
    and \\
    William Q. Meeker\footnotemark[1]}
  \maketitle
} \fi

@@

@@

\paragraph{Model 1} $\pi_{g} = \pi,\quad t_{p_{1}g} = t_{p1},\quad \sigma_{1g}=\sigma_1,\quad t_{p_{2}g} = t_{p2},\quad \sigma_{2g} = \sigma_2$
\paragraph{Model 2} $\pi_{g} = \pi,\quad t_{p_{1}g} = t_{p1},\quad \sigma_{1g}=\sigma_1,\quad \sigma_{2g} = \sigma_2$
\paragraph{Model 3} $\pi_{g} = \pi,\quad  t_{p_{1}g}= t_{p1},\quad \sigma_{1g}=\sigma_1$
\paragraph{Model 4} $t_{p_{1}g}= t_{p1},\quad \sigma_{1g}=\sigma_1$

@@

\paragraph{Model 1} Constrain all drive-models to the same GLFP distribution. For this ``reduced" model we assume the same prior distributions as in Example 1.

\paragraph{Model 2} $t_{p,g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p1} \sim \op{Lognormal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

\paragraph{Model 3} $t_{p,g}$ and $\sigma_{2g}$ vary by drive-model. Prior distributions for the constrained parameters are the same as for Model 2.

\paragraph{Model 4} $\pi_g$, $t_{p,g}$ and $\sigma_{2g}$ vary by drive-model. Prior distributions for constrained parameters are the same as for Model 2.

@@

\section{Comparing Sub-populations}
\subsection{Comparisons based on model parameters}
As discussed in Section \ref{sec:Weibull parameterization}, we use a parameterization of the Weibull distribution in terms of a chosen quantile, making prior elicitation straightforward. Posterior sampling immediately gives marginal posterior distributions for these quantiles, which in reliability applications is typically more informative than a measure of central tendency. If the selected model includes varying $t_{p2g}$ across sub-poputations, side-by-side plots of credible intervals provides a way to compare lifetime of non-defective units. Depending on a user's application, a similar plot for the $\pi_g$'s as a comparison tool may be a relevant parameter of interest.

\subsection{Example: Drive-model comparison based on quantiles and proportion defective}
The top panel of Figure 9 shows estimates of $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail, i.e. the quantile corresponding to the $H(t)$ distribution in Section \ref{subsec:GLFP model}), for all drive-models.  In this application 50\% CIs are more meaningful as there is lots of uncertainty in some of the parameters: especially for those with few drives in operation.  Interestingly, the top seven drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  Another interesting feature to compare is $\pi$, the proportion defective.  The bottom panel of Figure 9 shows the posterior credible intervals of $\pi$ for each drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the plot above.  While for many of the drive-models the ordinal ranking is the same as on the top, there are some drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10}$ or $\pi$.

>>>>

\if0\blind
{
  \title{\bf A Hierarchical Model for Heterogenous Reliability Field Data}
  \author{Eric Mittman, Colin Lewis-Beck, and William Q. Meeker\\
  Department of Statistics\\
  Iowa State University\\
  Ames, Iowa}
  \maketitle
} \fi

@@

Note that the $p$ quantile may be found by setting $p=H(t_p)$ and solving numerically for $t_p$.

@@

\paragraph{Model 1} $\pi_{g} = \pi,\quad t_{p_{1}g} = t_{p_1},\quad \sigma_{1g}=\sigma_1,\quad t_{p_{2}g} = t_{p_2},\quad \sigma_{2g} = \sigma_2$
\paragraph{Model 2} $\pi_{g} = \pi,\quad t_{p_{1}g} = t_{p_1},\quad \sigma_{1g}=\sigma_1,\quad \sigma_{2g} = \sigma_2$
\paragraph{Model 3} $\pi_{g} = \pi,\quad  t_{p_{1}g}= t_{p_1},\quad \sigma_{1g}=\sigma_1$
\paragraph{Model 4} $t_{p_{1}g}= t_{p_1},\quad \sigma_{1g}=\sigma_1$

@@

\paragraph{Model 1} Constrain all drive-models to the same GLFP distribution. For this ``reduced" model we assume the same prior distributions as in Section \ref{subsec:ex1}.

\paragraph{Model 2} $t_{p_{2}g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p_1} \sim \op{Lognormal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

\paragraph{Model 3} $t_{p_{2}g}$ and $\sigma_{2g}$ vary by drive-model. Prior distributions for the constrained parameters are the same as for Model 2.

\paragraph{Model 4} $\pi_g$, $t_{p_{2}g}$ and $\sigma_{2g}$ vary by drive-model. Prior distributions for constrained parameters are the same as for Model 2.

@@

\section{Comparing Sub-populations}
\subsection{Comparisons based on model parameters}
As discussed in Section \ref{sec:Weibull parameterization}, we use a parameterization of the Weibull distribution in terms of a chosen quantile, making prior elicitation straightforward. Posterior sampling immediately gives marginal posterior distributions for quantiles, which in reliability applications is typically more informative than a measure of central tendency. To compare the unconditional $p$ quantile for each sub-population, plots of posterior credible intervals may be used.

Depending on the set of model restrictions used, simlar plots may be used to compare the $p$ quantiles for non-defective units ($t_{p_{2}g}$) or the proportion defective ($\pi_g$).

\subsection{Example: Drive-model comparison based on quantiles and proportion defective}
The top panel of Figure 9 shows estimates of $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail, i.e. the quantile corresponding to the $H(t)$ distribution in Section \ref{subsec:GLFP model}), for all drive-models.  In this application 50\% CIs were used due to considerable posterior uncertainty in some of the parameters: especially for those with few drives in operation.  %Interestingly, the top seven drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  
Another interesting feature to compare is $\pi_g$, the proportion defective.  The bottom panel of Figure 9 shows the posterior credible intervals of $\pi_g$ for each drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the plot above.  While for many of the drive-models the ordinal ranking is the same as on the top, there are some drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10g}$ or $\pi_g$.
